Empirical normative theories

### 2020-07-21 simple.tex
Fixed def attack-exists
Impr wording of proof

Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeats \ar_0$ iff $\exists \hist \in \allhist \suchthat 
	\ar_1 \in (\gbeatsinv(\ar_0) \cap \hist) \land 
	(\gbeatsinv(\ar_0) \cap \hist) \setminus \set{\ar_1} \sinef \ar_0 \land 
	\ar_0 \in \histend \land 
	\hist \nileadsto \phi$.

@@

	Lemma: if $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \ar_1 \in \allargs, \ard_2 \in \allargs \suchthat \ard_2 \dbeats \ar_1 \ibeats \ar_0 \land \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard_2 \in \dip(\ar_0)$.
	Consider any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$ and $\ar_0 \nileadstost \phi$. 
	By definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhistsznp$.
	Because $\ar_0$ $i$-defends $\phi$, $\args^{\hist} ≠ \emptyset$. 
	From the preceding conclusion, we can pick some $\histp \in \allhistnonred$.
	Thus, $\exists \ar_1 \in \args^{\histp} \suchthat \args^{\histp} \setminus \set{\ar_1} \sinef \ar_0$.
	By definition, this means that $\ar_1 \ibeats \ar_0$ and, as $\ar_1 \in \args^{\histp} = \gbeatsinv(\ar_0) \cap \histp$, $\ar_1 \gbeats \ar_0$. 
	It now follows from the definition of an empirical theory that $\dbeatsinv(\ar_1)$ is not empty, thus, $\exists \ard_2 \in \allargs \suchthat \ard_2 \dbeats \ar_1$. Defining $\ar_2 = \ar_0 + \ard_2$, by definition of $\dip$, $\ar_2 \in \dip(\ar_0)$.

>>>>

Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeats \ar_0$ iff $\exists \hist \in \allhist \suchthat 
	\ar_1 \in (\gbeatsinv(\ar_0) \cap \hist) \land 
	(\gbeatsinv(\ar_0) \cap \hist) \setminus \set{\ar_1} \sinef \ar_0 \land 
	\ar_0 \in \histend \land 
	\hist \nileadstost \phi$.

@@

	Lemma: if $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \ar_1 \in \allargs, \ard_2 \in \allargs \suchthat \ard_2 \dbeats \ar_1 \ibeats \ar_0 \land \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard_2 \in \dip(\ar_0)$.
	Consider any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$ and $\ar_0 \nileadstost \phi$. 
	By definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhistsznp$.
	Because $\ar_0$ $i$-defends $\phi$, $\args^{\hist} ≠ \emptyset$. 
	From the preceding conclusion, we can pick some $\histp \in \allhistnonred$.
	Thus, $\exists \ar_1 \in \args^{\histp} \suchthat \args^{\histp} \setminus \set{\ar_1} \sinef \ar_0$.
	This shows that $\ar_1 \gbeats \ar_0$ and $\ar_1 \ibeats \ar_0$: 
		by definition of $\args^{\histp}$, $\ar_1 \in \gbeatsinv(\ar_0) \cap \histp$; and 
		$[\ar_0 \in \histp \land \histp \nileadstost \phi]$ follow from $\histp \in \allhistnonred$.
	It now follows from the definition of an empirical theory that $\dbeatsinv(\ar_1)$ is not empty, thus, $\exists \ard_2 \in \alldargs \suchthat \ard_2 \dbeats \ar_1$. Defining $\ar_2 = \ar_0 + \ard_2$, $\ar_2 \in \dip(\ar_0)$ by definition of $\dip$.
